### 2022-06-02 chapters/fairness/justicia/introduction.tex
all papers added
tables and figures updated with short caption

\section{Introduction}
%\paragraph{Motivation: \red{ML} + Fairness}
Machine learning is becoming the omnipresent technology of our time. Machine learning classifiers are being used for high-stake decisions like college admissions, crime recidivism, insurance, and loan decisions. Thus, human lives are now pervasively influenced by data, classifiers, and their inherent bias.

@@

\begin{figure}[t!]%%\vspace*{-1em}
	\centering\hspace*{-4em}
	\begin{minipage}{.33\columnwidth}
		\centering
		\scalebox{0.8}{	
			\begin{tikzpicture}[x=1.5cm,y=1.8cm]
			% Define nodes
			\node[latent,scale=1.5] (a1) {$\textrm{age}$} ; %
			\node[obs, scale=1.5, below=of a1, xshift=-.8cm] (h) {$\textrm{fitness}$}; %
			\node[obs, scale=1.5, below=of a1, xshift=.8cm] (i) {$\textrm{income}$}; %
			\node[obs, scale=1.5, below=of h, xshift=.8cm] (p) {$\hat{Y}$}; %			
			%%add edge
			\edge[] {a1} {h,i} ;
			\edge[] {h,i} {p} ;
			\end{tikzpicture}
		}
	\end{minipage}\hspace*{-2em}
	\begin{minipage}{.33\columnwidth}
		\centering
		\includegraphics[scale=0.5]{figures/fairness/justicia/example.pdf}
	\end{minipage}\hspace*{-2em}
	\begin{minipage}{.35\columnwidth}
		\scalebox{0.48}{	
			\begin{tikzpicture}[x=1cm,y=1.8cm]
			\node [box, scale=1.5]                                    (p)      {fitness $\geq 0.61$};
			\node [scale=1.5, above= 0.1cm of p]  (a)    {Trained Decision Tree};
			\node [scale=1.5, box, below= of p, xshift=-2.5cm]    (a1)    {income\\ $\geq 0.29$};
			\node [scale=1.5, box, below= of p, xshift=2.5cm]     (a2)    {income $\geq 0.69$};
			\node [scale=1.5,below= of a1, xshift=-1.8cm]  (a11)    { $\hat{Y}= 1$};
			\node [scale=1.5,below= of a1, xshift=1.8cm]   (a12)    { $\hat{Y}=0 $};
			\node [scale=1.5,below= of a2, xshift=-1.8cm]  (a21)    { $\hat{Y}= 1$};
			\node [scale=1.5,below= of a2, xshift=1.8cm]  (a22)    { $\hat{Y}= 0$};
			%
			\path [line] (p) -|         (a1) node [scale=1.5,midway, above]  {Yes};
			\path [line] (p) -|         (a2) node [scale=1.5,midway, above]  {No};
			\path [line] (a1) -|       (a11) node [scale=1.5,midway, above]  {Yes};
			\path [line] (a1) -|       (a12) node [scale=1.5,midway, above]  {No};
			\path [line] (a2) -|       (a21) node [scale=1.5,midway, above]  {Yes};
			\path [line] (a2) -|       (a22) node [scale=1.5,midway, above]  {No};
			\end{tikzpicture}}
	\end{minipage}%
	\caption{A trained decision tree to learn eligibility for health insurance using age-dependent fitness and income indicators.}\label{fairness_justicia_fig:fair_example}%\vspace*{-2em}
\end{figure}

>>>>

%\section{Introduction}
%\paragraph{Motivation: \red{ML} + Fairness}
Machine learning is becoming the omnipresent technology of our time. Machine learning classifiers are being used for high-stake decisions like college admissions, crime recidivism, insurance, and loan decisions. Thus, human lives are now pervasively influenced by data, classifiers, and their inherent bias.

@@

\begin{figure}
	\centering\hspace*{-4em}
	\begin{minipage}{.25\columnwidth}
		\centering
		\scalebox{0.6}{	
			\begin{tikzpicture}[x=1.5cm,y=1.8cm]
			% Define nodes
			\node[latent,scale=1.5] (a1) {$\textrm{age}$} ; %
			\node[obs, scale=1.5, below=of a1, xshift=-.8cm] (h) {$\textrm{fitness}$}; %
			\node[obs, scale=1.5, below=of a1, xshift=.8cm] (i) {$\textrm{income}$}; %
			\node[obs, scale=1.5, below=of h, xshift=.8cm] (p) {$\hat{Y}$}; %			
			%%add edge
			\edge[] {a1} {h,i} ;
			\edge[] {h,i} {p} ;
			\end{tikzpicture}
		}
	\end{minipage}\hspace*{-2em}
	\begin{minipage}{.33\columnwidth}
		\centering
		\includegraphics[scale=0.5]{figures/fairness/justicia/example.pdf}
	\end{minipage}\hspace*{-2em}
	\begin{minipage}{.35\columnwidth}
		\scalebox{0.48}{	
			\begin{tikzpicture}[x=1cm,y=1.8cm]
			\node [box, scale=1.5]                                    (p)      {fitness $\geq 0.61$};
			\node [scale=1.5, above= 0.1cm of p]  (a)    {Trained Decision Tree};
			\node [scale=1.5, box, below= of p, xshift=-2.5cm]    (a1)    {income\\ $\geq 0.29$};
			\node [scale=1.5, box, below= of p, xshift=2.5cm]     (a2)    {income $\geq 0.69$};
			\node [scale=1.5,below= of a1, xshift=-1.8cm]  (a11)    { $\hat{Y}= 1$};
			\node [scale=1.5,below= of a1, xshift=1.8cm]   (a12)    { $\hat{Y}=0 $};
			\node [scale=1.5,below= of a2, xshift=-1.8cm]  (a21)    { $\hat{Y}= 1$};
			\node [scale=1.5,below= of a2, xshift=1.8cm]  (a22)    { $\hat{Y}= 0$};
			%
			\path [line] (p) -|         (a1) node [scale=1.5,midway, above]  {Yes};
			\path [line] (p) -|         (a2) node [scale=1.5,midway, above]  {No};
			\path [line] (a1) -|       (a11) node [scale=1.5,midway, above]  {Yes};
			\path [line] (a1) -|       (a12) node [scale=1.5,midway, above]  {No};
			\path [line] (a2) -|       (a21) node [scale=1.5,midway, above]  {Yes};
			\path [line] (a2) -|       (a22) node [scale=1.5,midway, above]  {No};
			\end{tikzpicture}}
	\end{minipage}%
	\caption[A decision tree classifier on sensitive and non-sensitive features]{A trained decision tree to learn eligibility for health insurance using age-dependent fitness and income indicators.}\label{fairness_justicia_fig:fair_example}%\vspace*{-2em}
\end{figure}

### 2022-06-02 chapters/interpretability/imli/experiment.tex
all papers added
tables and figures updated with short caption

	\caption{Comparison of accuracy and rule-size among interpretable classifiers. Each cell from the fourth to the eighth column contains test accuracy (top) and rule-size (bottom). `\textemdash' represents a timeout. Numbers in bold represent the best performing results among different classifiers.}
	\label{interpretability_imli_table:interpretable_classifiers} 
	%	\setlength{\tabcolsep}{.2em}
	\small
	\begin{tabular}{lrrrrrrrrrrrr}

@@

	\subfloat{\includegraphics[scale=0.21]{figures/interpretability/imli/dataset_wdbc_cactus_train_val_fit_time}}
	\subfloat{\includegraphics[scale=0.21]{figures/interpretability/imli/dataset_adult_cactus_train_val_fit_time}}
	\subfloat{\includegraphics[scale=0.21]{figures/interpretability/imli/dataset_weatherAUS_cactus_train_val_fit_time}}
	\subfloat{\includegraphics[scale=0.21]{figures/interpretability/imli/dataset_labor_cactus_train_val_fit_time}}

	\caption{Comparison of scalability among interpretable classifiers. The plots are arranged in increasing sizes of datasets (from left to right). In each cactus plot, {\imli} solves all $ 1000 $ instances for each dataset, while competitive classifiers often fail to scale, specially in larger datasets.}
	\label{interpretability_imli_fig:interpretable_classifiers}
\end{figure}

@@

\begin{table*}[!t]        
	\centering
	\caption{Comparison of {\imli} with non-interpretable classifiers in terms of test accuracy. In the table, `\textemdash' represents a timeout. Numbers in bold represent the best performing results among different classifiers.}
	\label{interpretability_imli_table:non_interpretable_classifiers}
	%	\setlength{\tabcolsep}{.2em}
	\small
	\begin{tabular}{lrrrrrrrrrrrrrrr}

@@

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/imli_exp_wdbc_cactus_train_val_fit_time}}	
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/imli_exp_wdbc_cactus_test_accuracy}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/imli_exp_wdbc_cactus_predicate_count}}

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/imli_exp_credit_cactus_train_val_fit_time}}	
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/imli_exp_credit_cactus_test_accuracy}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/imli_exp_credit_cactus_predicate_count}}

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/imli_exp_adult_cactus_train_val_fit_time}}	
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/imli_exp_adult_cactus_test_accuracy}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/imli_exp_adult_cactus_predicate_count}}

	\caption{Comparison of training time, test error, and rule-size among different formulations presented in the paper. In each cactus plot, the incremental formulation {\imli} with both mini-batch and iterative learning demonstrates the best performance in training time and test error than compared two formulations: non-incremental MaxSAT formulation {\imli}-$\mathsf{B}$ and incremental formulation with only mini-batch learning {\imli}-$\mathsf{M}$. In terms of rule-size, {\imli} often generates higher size rules than {\imli}-$\mathsf{M}$.}
	\label{interpretability_imli_fig:different_formulations}
\end{figure}

@@

\begin{table*}[!t]        
	\centering
	\caption{Comparison of test accuracy (top value) and rule-size (bottom value) among different rule-based representations learned using {\imli}. Numbers in bold denote the best performing results among different representations.}
	\label{interpretability_imli_table:different_representations}
	%	\setlength{\tabcolsep}{.2em}
	\small
	\begin{tabular}{lrrrrrrrrrrrrrrr}

@@

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_test_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_train_val_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_predicate_count_wdbc}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_train_val_fit_time_wdbc}}

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_test_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_train_val_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_predicate_count_titanic}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_train_val_fit_time_titanic}}

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_test_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_train_val_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_predicate_count_adult}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/clauses_train_val_fit_time_adult}}

	\caption{Effect of the number of clauses $ k $ on accuracy (test and train), rule-size, and training time. As $ k $ increases, both train and test accuracy of {\imli} increase while generating rules with higher size by incurring higher training time. }
	\label{interpretability_imli_fig:effect_of_number_of_clauses}
\end{figure}

@@

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__test_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__train_val_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__predicate_count_wdbc}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__train_val_fit_time_wdbc}}

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__test_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__train_val_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__predicate_count_titanic}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__train_val_fit_time_titanic}}

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__test_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__train_val_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__predicate_count_adult}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/lambda__train_val_fit_time_adult}}

	\caption{Effect of regularization $ \lambda $ on accuracy (test and train), rule-size, and training time. As $ \lambda $ increases, lower priority is given to accuracy. As a result, both training and test accuracy decrease with $ \lambda $ by generating smaller rules. }
	\label{interpretability_imli_fig:effect_of_number_of_regularization}
\end{figure}

@@

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_test_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_train_val_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_predicate_count_wdbc}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_train_val_fit_time_wdbc}}

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_test_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_train_val_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_predicate_count_titanic}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_train_val_fit_time_titanic}}

	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_test_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_train_val_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_predicate_count_adult}}
	\subfloat{\includegraphics[scale=0.25]{figures/interpretability/imli/batch_size_train_val_fit_time_adult}}

	\caption{Effect of bath size on accuracy (test and train), rule-size, and training time. As we consider more samples in a mini-batch, {\imli} generates more accurate and larger size classification rules.}
	\label{interpretability_imli_fig:effect_of_batch_size}
\end{figure}

>>>>

	\caption[Accuracy and rule-size of interpretable classifiers]{Comparison of accuracy and rule-size among interpretable classifiers. Each cell from the fourth to the eighth column contains test accuracy (top) and rule-size (bottom). `\textemdash' represents a timeout. Numbers in bold represent the best performing results among different classifiers.}
	\label{interpretability_imli_table:interpretable_classifiers} 
	%	\setlength{\tabcolsep}{.2em}
	\small
	\begin{tabular}{lrrrrrrrrrrrr}

@@

	\subfloat{\includegraphics[scale=0.35]{figures/interpretability/imli/dataset_wdbc_cactus_train_val_fit_time}}
	\subfloat{\includegraphics[scale=0.35]{figures/interpretability/imli/dataset_adult_cactus_train_val_fit_time}}\\
	\subfloat{\includegraphics[scale=0.35]{figures/interpretability/imli/dataset_weatherAUS_cactus_train_val_fit_time}}
	\subfloat{\includegraphics[scale=0.35]{figures/interpretability/imli/dataset_labor_cactus_train_val_fit_time}}

	\caption[Scalability of Interpretable Classifiers]{Comparison of scalability among interpretable classifiers. The plots are arranged in increasing sizes of datasets (from left to right). In each cactus plot, {\imli} solves all $ 1000 $ instances for each dataset, while competitive classifiers often fail to scale, specially in larger datasets.}
	\label{interpretability_imli_fig:interpretable_classifiers}
\end{figure}

@@

\begin{table*}[!t]        
	\centering
	\caption[Accuracy of {\imli} and non-interpretable classifiers]{Comparison of {\imli} with non-interpretable classifiers in terms of test accuracy. In the table, `\textemdash' represents a timeout. Numbers in bold represent the best performing results among different classifiers.}
	\label{interpretability_imli_table:non_interpretable_classifiers}
	%	\setlength{\tabcolsep}{.2em}
	\small
	\begin{tabular}{lrrrrrrrrrrrrrrr}

@@

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/imli_exp_wdbc_cactus_train_val_fit_time}}	
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/imli_exp_wdbc_cactus_test_accuracy}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/imli_exp_wdbc_cactus_predicate_count}}

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/imli_exp_credit_cactus_train_val_fit_time}}	
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/imli_exp_credit_cactus_test_accuracy}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/imli_exp_credit_cactus_predicate_count}}

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/imli_exp_adult_cactus_train_val_fit_time}}	
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/imli_exp_adult_cactus_test_accuracy}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/imli_exp_adult_cactus_predicate_count}}

	\caption[Training time, test error, and rule-size of different formulations in {\imli}]{Comparison of training time, test error, and rule-size among different formulations presented in the paper. In each cactus plot, the incremental formulation {\imli} with both mini-batch and iterative learning demonstrates the best performance in training time and test error than compared two formulations: non-incremental MaxSAT formulation {\imli}-$\mathsf{B}$ and incremental formulation with only mini-batch learning {\imli}-$\mathsf{M}$. In terms of rule-size, {\imli} often generates higher size rules than {\imli}-$\mathsf{M}$.}
	\label{interpretability_imli_fig:different_formulations}
\end{figure}

@@

\begin{table*}[!t]        
	\centering
	\caption[Accuracy and rule-size of different classification rules learned using {\imli}]{Comparison of test accuracy (top value) and rule-size (bottom value) among different rule-based representations learned using {\imli}. Numbers in bold denote the best performing results among different representations.}
	\label{interpretability_imli_table:different_representations}
	%	\setlength{\tabcolsep}{.2em}
	\small
	\begin{tabular}{lrrrrrrrrrrrrrrr}

@@

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_test_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_train_val_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_predicate_count_wdbc}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_train_val_fit_time_wdbc}}

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_test_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_train_val_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_predicate_count_titanic}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_train_val_fit_time_titanic}}

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_test_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_train_val_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_predicate_count_adult}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/clauses_train_val_fit_time_adult}}

	\caption[Effect of the number of clauses in {\imli}]{Effect of the number of clauses $ k $ on accuracy (test and train), rule-size, and training time. As $ k $ increases, both train and test accuracy of {\imli} increase while generating rules with higher size by incurring higher training time. }
	\label{interpretability_imli_fig:effect_of_number_of_clauses}
\end{figure}

@@

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__test_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__train_val_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__predicate_count_wdbc}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__train_val_fit_time_wdbc}}

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__test_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__train_val_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__predicate_count_titanic}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__train_val_fit_time_titanic}}

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__test_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__train_val_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__predicate_count_adult}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/lambda__train_val_fit_time_adult}}

	\caption[Effect of regularization $ \lambda $ in {\imli}]{Effect of regularization $ \lambda $ on accuracy (test and train), rule-size, and training time. As $ \lambda $ increases, lower priority is given to accuracy. As a result, both training and test accuracy decrease with $ \lambda $ by generating smaller rules. }
	\label{interpretability_imli_fig:effect_of_number_of_regularization}
\end{figure}

@@

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_test_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_train_val_accuracy_wdbc}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_predicate_count_wdbc}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_train_val_fit_time_wdbc}}

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_test_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_train_val_accuracy_titanic}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_predicate_count_titanic}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_train_val_fit_time_titanic}}

	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_test_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_train_val_accuracy_adult}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_predicate_count_adult}}
	\subfloat{\includegraphics[scale=0.3]{figures/interpretability/imli/batch_size_train_val_fit_time_adult}}

	\caption[Effect of batch-size in {\imli}]{Effect of bath size on accuracy (test and train), rule-size, and training time. As we consider more samples in a mini-batch, {\imli} generates more accurate and larger size classification rules.}
	\label{interpretability_imli_fig:effect_of_batch_size}
\end{figure}
